---
title: "Returns 6/0/6 Sector Momentum"
author: "Tom Marty"
output: 
  html_document:
    code_folding: hide
    theme: yeti  #lumen, paper, sandstone, simplex, yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up
Load packages and functions.
```{r message=FALSE, results='hide'}
library(xts)
library(lubridate)
library(PerformanceAnalytics)
library(readr)
library(TTR)
library(RColorBrewer)
library(blotter)
library(FinancialInstrument)
library(parallel)
library(foreach)
library(doParallel)
library(kableExtra)
dataDir <- "~/Desktop/Momentum_tests/Bruce/data"
functionDir <- "/home/ito/Desktop/PhD/Other_Courseware/trademartyr/R"
sapply(file.path(functionDir,list.files(functionDir)),source,echo=FALSE)
Sys.setenv(TZ = "UTC")
```

Load data and create an xts of close prices and another of returns. 
The `clean_names` function just changes the names of the OHLC data for each of
the assets, since the default names from Bloomberg are not recognised by
blotter. The function also provides functionality for using adjusted returns
and preserving an index membership column if required.

```{r message=FALSE, cache=TRUE}
assets <- gsub(".csv","",list.files(dataDir))
load_files(dataDir,list.files(dataDir))
clean_names(assets)
DF <- get_cols(assets,"Close") # Prices
DF_rets <- na.fill(simpleRets(DF),0) # Returns
```

## Strategy parameters
Set strategy parameters. 

```{r message=FALSE}
TopN = 1
nassets=length(assets)
J_m=6
S_m=0
K_m=6
starting_capital=1e06
initEq <- starting_capital/K_m
```

## Generate positions
Perform momentum ranking and get position weights for simple equal-weighted 
long-short portfolio. Note that we can pass several formation periods to 
`mom_rank` and it will rank based on acceleration--the average of the momentum 
of the specified formation periods.

```{r message=FALSE}
mom <- mom_rank(DF, on="months", n=J_m, S=S_m)
weights <- get_weights_ls(mom, TopN=TopN)
```

We can visualise the proposed entries and exits. This is probably only useful 
when dealing with a small number of assets. Exits are shown in brackets.

```{r message=FALSE}
trades <- visualise_trades(weights, K_m)
```

```{r echo=FALSE}
scroll_box(kable_styling(column_spec(kable(trades,caption="Ranks"),column = 1, 
                                     width = "2.5cm"),
                         bootstrap_options=c("striped","bordered")), 
           width = "100%", height="200px")
```

## Return-based simulation
As with all of our approaches, each of the K overlapping portfolios are 
simulated separately. The `holding_time` parameter just indicates that we don't 
enter a trade unless there is enough time left (in the data) to fulfill the 
entire holding period.

```{r , cache=TRUE}
return_list <- list()
for (start_i in 1:K_m){
  wts_i <- weights_i(weights, start_i, K_m, holding_time=TRUE )[[1]]
  rp <- portfolio_cumulative.return(DF_rets, weights=wts_i)
  return_list[[start_i]] <- initEq*rp
  names(return_list)[start_i] <- paste0("P",start_i)
}
rp_mat <- do.call(cbind, return_list); names(rp_mat) <- names(return_list)
```

## Blotter simulation
When blotter references transaction and portfolio objects using a date range, it
adjusts the righthand date such that it has a time of 23:59:59 ( specifically
it uses a call like this `.parseISO8601(date_range)$last.time`. If the righthand
date happens to be the last date in the data, blotter will throw a warning
because it looks like we have asked for a date that isn't in the asset xts
objects. There are a few ways to avoid this the safest is simply to,
apped an extra day to to each of the objects. It doesn't matter that it will be
empty as it won't be referenced.
```{r }
# Append 1 day extra to avoid annoying blotter range warning
for (i in 1:length(assets)){
  x <- get(assets[i])
  x <- cbind(x,index(x)[nrow(x)]+days(1))
  assign(assets[i], x)
}
```

Set common blotter parameters.

```{r message=FALSE, results='hide'}
Currency="USD"
currency(Currency)
stock(assets,currency = Currency)
enter_prefer="Close"
exit_prefer="Close"
ind <- index(weights)
initdate <- ind[1] - days(1)
enddate <- ind[length(ind)]
```

We perform the simulation in parallel. Blotter and financial instrument are
called within each of the parallel environments, and the currency and stock
instruments are loaded into whatever environment  the `FinancialInstrument`
package sends them. If this is not done, blotter can't find them when updating
the portfolios.

```{r message=FALSE, results='hide', cache=TRUE}
cores <- detectCores()
mycluster <- makeCluster(cores-1,type = "FORK")
registerDoParallel(mycluster)
out <- foreach(
  start_i = 1:K_m) %dopar% {
    library(blotter)
    library(FinancialInstrument)
    currency(Currency)
    stock(assets,currency = Currency)
    place_transactions(initEq, assets, Currency, ind, start_i=start_i, K_m,
                             wts=weights, initdate, enddate, holding_time=TRUE)
  }
stopCluster(mycluster)
```

### Extract blotter results

```{r message=FALSE, results='hide', cache=TRUE}
# Load portfolios into environment
portf_names <- list()
for (i in 1:length(out)){
  portf_names[[i]] <- names(out[[i]])
  put.portfolio(names(out[[i]]),out[[i]][[1]])
}
# Create combined account from individual portfolios
accountName=paste0("acct_",J_m,S_m,K_m)
suppressWarnings(rm(list=c(paste0("account.",accountName)), pos=.blotter))
initAcct(name=accountName, portfolios=portf_names, initDate=initdate,
         initEq=starting_capital)
updateAcct(accountName)
updateEndEq(accountName)
```

We can also view the actual transactions to make sure they are consistent with
what we expected.

```{r message=FALSE, cache=TRUE}
txns <- txn_pretty(portfolio_list = unlist(portf_names))
```

```{r echo=FALSE}
scroll_box(kable_styling(kable(txns),bootstrap_options =c("striped","bordered"))
           ,width = "100%",height="600px")
```

## Compare results
We compare each of the individual K portfolios.
```{r message=FALSE, warning=FALSE, results='hide', cache=TRUE}
# Me - blotter
acct <- getAccount(accountName)
# Bruce - blotter
b_rets <- read_csv(file.path("~/Desktop/Momentum_tests/Bruce",
                             "Bruces_returns.csv"))
b_rets <- xts(b_rets[,-1],order.by = b_rets$X1)
b_eq <- initEq*cumprod(1+b_rets[,1:K_m])
```

```{r fig.width=10}
# Compare individual portfolios
par(mfrow = c(K_m/2, 2))
par(oma = c(4, 4, 0, 0))
par(mar = c(0.25, 0.25, 0.25,.25))
ylim=c(0.5e05,6e05)
for(n in 1:K_m){
  b_ind <- index(b_rets)[b_rets[,n]!=0]
  eq_t <- out[[n]][[1]]$summary$Gross.Trading.PL
  eq_t[1] <- initEq
  eq_r <- rp_mat[,n]
  Yaxt="n"
  Xaxt="n"
  Ylab=""
  if(n %% 2 != 0){
    Yaxt="t"
  }
  if(n > K_m-2){
    Xaxt="t"
  }
  plot.zoo(cbind(b_eq[,n],cumsum(eq_t), eq_r)[b_ind],
           col =c("darkorange3","cyan4","black") ,screens = 1,
           lty=c("solid", "dashed", "dotted"),
           lwd=2, xlab="", ylab="", xaxt=Xaxt, yaxt=Yaxt, ylim = ylim)
  legend("topleft",legend = c("Bruce","Tom", "return-based"),lwd=2,
         col=c("darkorange3","cyan4", "black"),
         lty=c("solid","dashed","dotted"), cex=1)
  if(n==trunc(K_m/2)){
    mtext(paste("Equity ($)"), side = 2, line = 2.2, adj = 0.5, cex = 1,
          col = "black")
  }
  mtext(paste("Portfolio",n), side = 3, line = -1.5, adj = 0.5, cex = .8,
        col = "black")
}
```

Here we compare combined portfolios. Bruces looks different because he updated 
his portfolios on different dates (only at transactions), so the curve only 
shows fluctuations from one portfolio at a time (and only on months).

```{r fig.width=10}
par(mfrow = c(1,1))
t_port <- acct$summary$End.Eq
b_port <- xts(rowSums(b_eq),order.by=index(b_eq))
r_port <- xts(rowSums(rp_mat),index(rp_mat))
plot.zoo(cbind(b_port,t_port, r_port)[index(b_port)],
         col =c("darkorange3","cyan4","black") ,screens = 1,
         lty=c("solid", "dashed", "dotted"),
         lwd=2, xlab="", ylab="Account Equity", main = "Combined Portfolio")
legend("topleft",legend = c("Bruce","Tom", "return-based"),lwd=2,
       col =c("darkorange3","cyan4", "black"), lty=c("solid","dashed","dotted"),
       cex=0.8)

```

Here we compare Tom's blotter results with the return-based results at a greater 
granularity (daily).
```{r fig.width=10}
plot.zoo(cbind(t_port, r_port),
         col =c("cyan4","black") ,screens = 1,
         lty=c("dashed", "dotted"),
         lwd=2, xlab="", ylab="Account Equity", main = "Combined Portfolio")
legend("topleft",legend = c("Tom", "return-based"),lwd=2,
       col =c("cyan4", "black"), lty=c("dashed","dotted"),
       cex=0.8)

```



<!-- ## Results -->
<!-- View the positions for each of the overlapping portfolios. -->

<!-- ```{r } -->
<!-- scroll_box(kable_styling(kable(tb),bootstrap_options =c("striped","bordered")) -->
<!--            ,width = "100%",height="600px") -->
<!-- ``` -->

<!-- View results. -->

<!-- ```{r figure.width=7,out.width='100%',eval=TRUE,echo=TRUE} -->
<!-- darkcols <- brewer.pal(K_m,"Dark2") -->
<!-- plot.zoo(cumprod(1+na.fill(Strat_list,0)),col = darkcols,screens = 1, -->
<!--          xlab="",ylab="Cumulative Return",main="Individual Overlapping Portfolios") -->
<!-- legend("topleft",legend = paste0("K_",1:K_m),lwd=1,col = darkcols,cex=0.8) -->
<!-- ``` -->

<!-- ```{r ,figure.width=7,out.width='100%',message=FALSE,eval=TRUE,echo=TRUE} -->
<!-- RP <- Return.portfolio(na.fill(Strat_list,0)) # Not just overlapping portion -->
<!-- plot.zoo(cumprod(1+RP), col = "black",screens = 1, lwd=2, -->
<!--          xlab="",ylab="Cumulative Return",main="Combined Overlapping Portfolio") -->
<!-- ``` -->

<!-- ```{r ,figure.width=7,out.width='100%',message=FALSE,eval=TRUE,echo=TRUE} -->
<!-- setCols <- brewer.pal(nassets+1,"Paired") -->
<!-- setCols[nassets+1] <- "black" -->
<!-- plot.zoo(cumprod(1+na.omit(cbind(DF_rets,RP))), col = setCols,screens = 1, lwd=2, -->
<!--          xlab="",ylab="Cumulative Return",main="Assets") -->
<!-- legend("topleft",legend = c(names(DF_rets),"Strategy"),lwd=2, -->
<!--        col=setCols,cex=0.8) -->
<!-- ``` -->

<!-- ```{r figure.width=7,out.width='100%',eval=TRUE,echo=TRUE} -->
<!-- RP_long <- Return.portfolio(na.fill(Long_list,0)) # Not just overlapping portion -->
<!-- RP_short <- Return.portfolio(na.fill(Short_list,0)) # Not just overlapping portion -->
<!-- BH <- Return.portfolio(cbind(RP_long,RP_short)) -->
<!-- plot.zoo(cumprod(1+cbind(RP_long,RP_short,BH)),col = c("cyan4","darkorange3","black"),screens = 1, -->
<!--          xlab="",ylab="Cumulative Return",main=" Buy-and-hold Long and Short Legs",  -->
<!--          lwd=2) -->
<!-- legend("topleft",legend = c("Long side","Short side","Buy-hold combined"),lwd=2, -->
<!--        col=c("cyan4","darkorange3","black"),cex=0.8) -->
<!-- ``` -->

<!-- ## Extra -->
<!-- Below I plot the portfolio that would result if the long and short legs were treated  -->
<!-- as equal-weighted buy and hold positions (above), in relation to the other assets.  -->
<!-- This is a bit closer to Bruce's result which makes no sense to me.  -->

<!-- ```{r ,figure.width=7,out.width='100%',message=FALSE,eval=TRUE,echo=TRUE} -->
<!-- plot.zoo(cumprod(1+na.omit(cbind(DF_rets,BH))), col = setCols,screens = 1, lwd=2, -->
<!--          xlab="",ylab="Cumulative Return",main="Assets") -->
<!-- legend("topleft",legend = c(names(DF_rets),"Buy-hold combined"),lwd=2, -->
<!--        col=setCols,cex=0.8) -->
<!-- ``` -->
